---
title: "maxnetic"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Maxnetic](https://github.com/BigelowLab/maxnetic) provide supplementary tools to augment the [maxnet](https://CRAN.R-project.org/package=maxnet) package.

Information about ROC and AUC were gleaned from the [Receiver operating characteristic](# https://en.wikipedia.org/wiki/Receiver_operating_characteristic) wikipedia page.

### Requirements

 + [R v 4.1+](https://www.r-project.org/)
 + [dplyr](https://CRAN.R-project.org/package=dplyr)
 + [ggplot2](https://CRAN.R-project.org/package=ggplot2)


### Installation

```
remotes::install_github("BigelowLab/maxnetic")
```

### Functionality

 + `TPR()` true positive rate, 
 + `FPR()` false positive rate 
 + `ROC()` receiver operator values 
 + `AUC()` compute are under curve of ROC
 + `plot()` plot an `ROC` class object (base graphics or gpplot2)
 + `write_maxnet()` and `read_maxnet()` for IO to R's serialized file format


### Usage

```{r load}
suppressPackageStartupMessages({
  library(dplyr)
  library(maxnet)
  library(maxnetic)
  library(ggplot2)
})
```

Next we load data, make a model and then a data frame with the input labels and the output prediction.


```{r gather_results}
obs <- dplyr::as_tibble(maxnet::bradypus)

mod <- maxnet(obs$presence, dplyr::select(obs, -presence))
pred <- predict(mod, newdata = bradypus, na.rm = TRUE, type = "cloglog")

x <- dplyr::tibble(pres = obs$presence,
                   pred = pred[,1])
dplyr::glimpse(x)
```


Collect the responses.

```{r collect_response}
r <- plot(mod, type = "cloglog", plot = FALSE)
ok = lapply(r, str)
```

Plot the response curves

```{r plot_response}
p = gather_plots(r)

p
```

Now compute ROC and show

```{r roc}
roc <- ROC(x)
plot(roc, use = "base", title = "Base Graphics")
plot(roc, use = "ggplot", title = "ggplot2")
```