---
title: "maxnetic"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Maxnetic](https://github.com/BigelowLab/maxnetic) provide supplementary tools to augment the [maxnet](https://CRAN.R-project.org/package=maxnet) package.

Metrics like, TPR, FPR, ROC and AUC are all computed with the [AUC](https://CRAN.R-project.org/package=AUC) R package.

### Requirements

 + [R v 4.1+](https://www.r-project.org/)
 + [AUC](https://CRAN.R-project.org/package=AUC)
 + [dplyr](https://CRAN.R-project.org/package=dplyr)
 + [ggplot2](https://CRAN.R-project.org/package=ggplot2)


### Installation

```
if (!("AUC" %in% rownames(installed.packages())) install.packages("AUC")
remotes::install_github("BigelowLab/maxnetic")
```

### Functionality

 + `TPR()` true positive rate ("sensitivity") 
 + `FPR()` false positive rate ("specificity")
 + `ROC()` receiver operator values 
 + `AUC()` compute are under curve of ROC
 + `plot_ROC()` plot an `ROC` class object (base graphics or gpplot2)
 + `write_maxnet()` and `read_maxnet()` for IO to R's serialized file format

### Usage

```{r load}
suppressPackageStartupMessages({
  library(maxnet)
  library(dplyr)
  library(maxnetic)
  library(ggplot2)
})
```

Next we load data, make a model and then a data frame with the input labels and the output prediction.


```{r gather_results}
obs <- dplyr::as_tibble(maxnet::bradypus)

mod <- maxnet(obs$presence, dplyr::select(obs, -presence))
pred <- predict(mod, newdata = bradypus, na.rm = TRUE, type = "cloglog")

x <- dplyr::tibble(label = obs$presence,
                   pred = pred[,1])
dplyr::glimpse(x)
```


Collect the responses.

```{r collect_response}
r <- plot(mod, type = "cloglog", plot = FALSE)
```

Plot the response curves

```{r plot_response}
plot(mod, type = 'cloglog', mar = c(2,2,2,1))
```

Now compute ROC and show using either base or ggplot2 graphics.

```{r roc}
plot_ROC(x, use = "base", title = "Base Graphics")
plot_ROC(x, use = "ggplot", title = "ggplot2 Graphics")
```