---
title: "maxnetic"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Maxnetic](https://github.com/BigelowLab/maxnetic) provide supplementary tools to augment the [maxnet](https://CRAN.R-project.org/package=maxnet) package.


### Requirements

 + [R v 4.1+](https://www.r-project.org/)
 + [AUC](https://CRAN.R-project.org/package=AUC)
 + [dplyr](https://CRAN.R-project.org/package=dplyr)
 + [ggplot2](https://CRAN.R-project.org/package=ggplot2)
 + [Rfast](https://CRAN.R-project.org/package=Rfast)
 + [stars](https://CRAN.R-project.org/package=stars)

### Installation

```
needed = c("AUC", "stars", "Rfast", "dplyr", "ggplot2")
installed = rownames(installed.packages())
for (need in needed) {
  if (!(need %in% installed)) install.packages(need)
}
remotes::install_github("BigelowLab/maxnetic")
```

### Functionality

#### Presence only datasets
  + `pAUC()` for computing AUC for presence points only (aka forecasted AUC or fAUC)
  + `plot`, a method to plot `pAUC` objects

#### Presence-Absence datasets

 + `TPR()` true positive rate ("sensitivity") 
 + `FPR()` false positive rate ("specificity")
 + `ROC()` receiver operator values 
 + `AUC()` compute are under curve of ROC
 + `plot_ROC()` plot an `ROC` class object (base graphics or gpplot2)
 
#### General purpose utility
 
 + `write_maxnet()` and `read_maxnet()` for IO to R's serialized file format

### Usage

```{r load}
suppressPackageStartupMessages({
  library(maxnet)
  library(dplyr)
  library(maxnetic)
  library(ggplot2)
})
```

Next we load data, make a model and then a data frame with the input labels and the output prediction.


```{r gather_results}
obs <- dplyr::as_tibble(maxnet::bradypus)

model <- maxnet(obs$presence, dplyr::select(obs, -presence))
pred <- predict(model, newdata = bradypus, na.rm = TRUE, type = "cloglog")

x <- dplyr::tibble(label = obs$presence,
                   pred = pred[,1])
dplyr::glimpse(x)
```


Collect the responses.

```{r collect_response}
r <- plot(model, type = "cloglog", plot = FALSE)
```

Plot the response curves

```{r plot_response}
plot(model, type = 'cloglog', mar = c(2,2,2,1))
```

Now compute ROC and show.

```{r roc}
roc = ROC(x)
plot(roc, title = "Bradypus model")
```

You can also compute a "presence AUC" which involves only the presence points. Unlike a ROC object, a pAUC object has it's own plot method.

```{r pauc}
p = dplyr::filter(x, label == 1)
pauc = pAUC(x$pred, p$pred)
plot(pauc)
```

You might be wondering why have pAUC if AUC already exists.  AUC is used where you have both presence and absence data.  For presence only data we need to use a modified computation.